---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

languagelayeR is now on [CRAN](https://CRAN.R-project.org/package=languagelayeR)

[![Travis build status](https://travis-ci.org/ColinFay/languagelayeR.svg?branch=master)](https://travis-ci.org/ColinFay/languagelayeR)   [![Coverage status](https://codecov.io/gh/ColinFay/languagelayeR/branch/master/graph/badge.svg)](https://codecov.io/github/ColinFay/languagelayeR?branch=master)


# languagelayerR

This package is designed to detect a language from a character string in R by acessing the languagelayer API — https://languagelayer.com/

## Language layer API 

This package offers a language detection tool by connecting to the languagelayer API, a JSON interface designed to extract language information from a character string. 

## Install languagelayerR

Install this package directly in R : 

From CRAN : 

```{r eval = FALSE}
install.packages("languagelayeR")
```

From Github :

```{r eval = FALSE}
devtools::install_github("ColinFay/languagelayeR")
```

## How languagelayeR works

The version 1.1.0 works with two functions. Which are :  

* `get_lang` Get language information from a character string

* `get_supported_lang` Get all current accessible languages on the languagelayer API


## First of all

Before any request on the languagelayer, you need to get your API key from your language layer [dashboard](https://languagelayer.com/dashboard).

## Examples 

### getLanguage 

Detect a language from a character string. 

```{r eval = FALSE}
get_lang(query = "I really really love R and that's a good thing, right?", api_key = "your_api_key")
```

### getSupportedLanguage 

List all the languages available on the languagelayer API. 

```{r eval = FALSE}
get_supported_lang(api_key = "your_api_key")
```

### Contact

Questions and feedbacks [welcome](mailto:contact@colinfay.me) !

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md).
By participating in this project you agree to abide by its terms.
